Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-01-29 template.tex
updated the pdf

Completing the square in the exponent, and letting $x = (t-t_0)/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find

@@

\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I(x,z_0)} \\
\Aboxed{I(x,z_0) &= \int_0^{\infty} \frac{y e^{(x+jy)^2}}{y-z_0} dy}

@@

However, approximating $I(x,z_0) \approx I(x,0)$ drops the dependance on $\gamma$ and $f_0$.  Voigt or Faddeeva functions can be introduced, if only the denominator was even in $y$.  This suggests rationalizing the denominator:
\frac{1}{y-z_0} = \frac{\frac{f-f_0}{\sqrt{2}\sigma_f} - \frac{j\gamma}{2\pi\sqrt{2}\sigma_f}}{\frac{(f-f_0)^2}{2\sigma_f^2} + \frac{\gamma^2}{4\pi^2 2\sigma_f^2}}

>>>>

Completing the square in the exponent, and letting $x = (t-t_0)/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z_0 \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find

@@

\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I(x,z_0)} \label{eq:end1} \\
\Aboxed{I(x,z_0) &= \int_0^{\infty} \frac{y e^{(x+jy)^2}}{y-z_0} dy} \label{eq:end2}

@@

However, approximating $I(x,z_0) \approx I(x,0)$ drops the dependance on $\gamma$ and $f_0$.
\item To solve Eq. \ref{eq:end2}, the integral function is expanded in powers of $z_0$.  This is wise, given that the UHE-$\nu$ signal bandwidth will usually exceed that of a dipole receiver with response $r(t)$ and analytic signal $r_a(t)$.
